Brouillon PoF,PRF..

### 2019-02-07 draft_p2.tex
Adds new figures to draft

\documentclass[pre,aps,floatfix,10pt,superscriptaddress, notitlepage]{revtex4-1}
\pdfoutput=1
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage[svgnames]{xcolor}
\usepackage{graphicx}
\usepackage{acro}
\usepackage{subfig}
\usepackage{caption}
\graphicspath{{../figures/}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{illustration_vorticity_tf2}
  \caption{Typical vorticity field in the computational domain. The square obstacle is represented by the gray area in the center of the channel.}
\end{figure}
%% Description de la géométrie
We consider the interaction of a two dimensional turbulent channel flow with a square cylinder, illustrated in figure~\ref{fig:computational_domain}.
A constant parabolic velocity profile is imposed at the inlet of the channel and turbulence is
generated by means of a grid.
A square obstacle is mounted at the center of the channel.
Eddies are created in the vicinity of the grid with a typical size that correspond to the step of the grid.
As they are advected downstream, eddies interact with each other and grow in size, until they interact with the obstacle.
The distance separating the obstacle from the grid is such that the typical size of the eddies it interacts with is close to the size of the obstacle itself.
The flow in the vicinity of the outlet is regularized by means of a \textit{sponge layer}~\cite{ref1,ref2}, \textit{i.e.} a region where the viscosity is progressivaly increased.
Such sponge layer facilitates the implementation of an open boundary at the outlet, where a zero momentum flux along the mean-flow direction in imposed.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{illustration_signal_drag_1}
  \caption{Typical temporal evolution of the drag acting on the square cylinder pictured in figure~\ref{fig:computational_domain}. The correlation time $\tau_c$ is defined further in this text and correspond to the typical fluctuation timescale of the drag.}
  \label{fig:typical_drag_signal}
\end{figure}

@@

\begin{figure}
  \centering
    \subfloat[\ac{pdf} for the drag fluctuations $f'_d$]{\label{fig:pdf_drag_a}\includegraphics[width=.5\linewidth]{../figures/pdf_drag_SQ_asymetry_expo}}
    \subfloat[Autocorrelation function of the the instantaneous drag $f_d$]{\label{fig:pdf_drag_b}\includegraphics[width=.5\linewidth]{../figures/correlation_with_log}}  
  \caption{\textbf{(a)} \ac{pdf} describing the statistics of the instantaneous drag fluctuations $f'_d = (f_d - \bar{f_d})/\sigma$. This \ac{pdf} has been estimated on the basis of a timeseries spanning $T_{tot} = 10^6 \tau_c$. $\bar{f_d}$ and $\sigma$ denote the average and the standard deviation computed over the whole timeseries, respectively. The linear fits highlight the exponential behaviour of the the \ac{pdf} for rare events. \textbf{(b)} Autocorrelation function for the instantaneous drag $f_d$, defined as $(\mathbb{E}[f_d(t+\tau)f_d(t)]-\mathbb{E}[f_d]^2)/\sigma^2$ and estimated from a timeseries spanning $T_{tot} = 10^6 \tau_c$. This figure shows the exponential decay of the correlations over time.}
  \label{fig:pdf_drag}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.6\linewidth]{return_time_drag}
  \caption{Drag fluctuation amplitude as a function the corresponding return time. The return time $r(a)$ is the typical timescale of occurrence of a fluctuation of amplitude larger than $a$.}
  \label{fig:return_time_instant}
\end{figure}
\subsection{Instantaneous drag}
\label{sec:instantaneous_drag}

\subsubsection{Contribution of forebody and base pressure fluctuations to the overall drag fluctuation}
\label{sec:forebody_and_base_contribution}
In section~\ref{sec:test_flow}, we pointed out that typical drag fluctuations mainly originate from fluctuations of the forebody pressure, \textit{i.e.} pressure fluctuations resulting from the upstream turbulent flow.
We now investigate the relative contribution of forebody and base pressure fluctuations to the overall drag fluctuations, in the case of the sampled \textit{extreme} drag fluctuations.
Let $(t^{\star}, f_d^{\star})$ be an extreme drag event.
In the following we consider the effective fluctuation $\tilde{f}_d^{\star} = f_d^{\star} - \langle f_d \rangle$.
It can be further decomposed into 
\begin{equation}
  \tilde{f}_d^{\star} = \tilde{p}_{fb}^{\star} - \tilde{p}_{base}^{\star},
\end{equation}
where $\tilde{p}_{fb}^{\star}$ and $\tilde{p}_{base}^{\star}$ denote the fluctuation of the forebody pressure and base pressure, respectively, that is $\tilde{p}_{base}^{\star} = p_{base}^{\star} - \langle p_{base} \rangle$ .
Figure~\ref{fig:contribution_forebody_and_base_pressure} shows the relative contributions $\tilde{p}_{base}^{\star}/\tilde{f}_d^{\star}$ and $\tilde{p}_{fb}^{\star}/\tilde{f}_d^{\star}$ to the overall drag fluctuation for the base and forebody pressure fluctuations, respectively.  
\begin{figure}
  \centering
  \label{fig:contribution_forebody_and_base_pressure}
\end{figure}
It shows that among the 104 sampled extreme events, the base pressure fluctuation typically contributes for $80\%$ of the overall drag fluctuation.
By contrast with typical drag fluctuations, extreme fluctuations of the drag acting on the square cylinder are dominated by the variation of the pressure in the vicinity of the base of the obstacle.
In addition, figure~\ref{fig:contribution_forebody_and_base_pressure} hints that, the larger the fluctuation, the more important is the contribution of the base pressure fluctuation, relatively to the forebody pressure fluctuation.

@@

\begin{figure}
  \centering
  \begin{minipage}{0.85\linewidth}
    \begin{tabular}{c|c}
    \subfloat[$f'_d = 11.6\sigma$]{\label{fig:top_4_events_vorticity_a}\includegraphics[width=0.4\linewidth]{event_95_vort.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$f'_d = 11.2\sigma$]{\includegraphics[width=0.4\linewidth]{event_69_vort.png}} \\
    \hline
    \subfloat[$f'_d = 10.6\sigma$]{\includegraphics[width=0.4\linewidth]{event_53_vort.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$10\sigma$]{\includegraphics[width=0.4\linewidth]{event_20_vort.png}}
    \end{tabular}
  \end{minipage}
\begin{minipage}[h]{0.1\linewidth}
  \centering
  \includegraphics[width=\linewidth]{scale_vorticity.png}
\end{minipage}
\caption{\label{fig:top_4_events_vorticity} Vorticity field at $t=t^{\star}$ for the four highest drag fluctuations in the timeseries. The corresponding drag timeseries can be found in figure~\ref{fig:extremes_timeseries}.
  The high value for the drag results from the formation of a strong negative (red) vortex inducing a pressure drop at the base of the obstacle. The formation of such a structure is aided by important vorticity production at the bottom boundary of the obstacle coupled with the influence of positive vorticity in the vicinity of the base.}
\end{figure}

@@

% Modify the TAMS to fit the phenomenology ?
A promising perspective is to adapt the \ac{tams} to dynamics for which the Lyapunov time is larger than the typical duration of extreme events, such as the convective flow involved in this work.
In the original \ac{tams}, at later stages of the algorithm, new trajectories are resampled starting from points very close to the maximum of the parent trajectory.
Resampled trajectories have no chance to display a significantly higher maximum as they overlap their parent trajectory over the Lyapunov timescale.
As an example, the resampling procedure could be modified so that new trajectories are resampled roughly a Lyapunov time \textit{before} the maximum is attained.
In this way, it gives the opportunity for new events, associated to a higher fluctuations, to occur.
However, such modification(s) of the resampling procedure must be implemented with care, so as to preserve the mathematical properties of the \ac{ams} and \ac{tams}.
\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{ams/figure_AMS}
  \caption{Illustration of one selection-mutation step in the \ac{ams} algorithm for the computation of the probability that an observable $A:\mathbb{R}^d\to \mathbb{R}$  reaches values larger than $Q$ over a trajectory of duration $T_a$.}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{ams/comparaison_temps_de_retour}
    \caption{Illustration of the efficiency of the \ac{tams} algorithm with respect to direct sampling. The amplitude of fluctuations for the \ac{ou} process~\eqref{eq:OUprocess_chap_ams} are represented along the Y-axis. Along the X-axis is represented the typical computational cost required to sample fluctuations of the corresponding amplitude in both the \ac{tams} and direct sampling. In the latter, the typical computational cost is simply the return time $r(a)$. The computational cost associated to a level $a$ is the \ac{tams} is denoted by $C(a)$. The orange line represents the evolution of the level $\mathcal{Q}_j^{\star}$ as a function of the cost $C(a)$. The blue stars represent the maximum of $x(t)$ over the resampled trajectory \emph{after} it is resampled, that is at iteration $j+1$. Finally, the solid black line is the analytical solution for the return time of amplitude $a$~\cite{lestang_computing_2018}.}
  \label{fig:comparaison_temps_de_retour}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{ams/instant_256_20}
    \caption{Maximum of the instantaneous drag along the resampled trajectories, denoted by $\tilde{f}_d^{(j)}$, as a function of the corresponding computational cost $C_j$, defined in~\eqref{eq:comp_cost_iterations}. In both figures, the \ac{tams} is iterated until extinction. 
    The solid black line indicates the typical fluctuation amplitude $a$ as a function of the corresponding  \textit{return time} $r(a)$. It is the typical timescale of occurrence of fluctuations above $a$. Furthermore, the square markers depict the maximum $\tilde{f}_{d,n}^{(0)},\,\, 1\leq n \leq N_c$ over the initial trajectories.
    This figure illustrates that in both experiments the \ac{tams} does not improve the sampling of rare fluctuations. On can see that the maximum values among the resampled trajectories concentrates on values already sampled over the initial trajectories. Eventually, extinction is reached as the algorithm is unable to generate a fluctuation higher than the maximum fluctuation in the initial ensemble of trajectories.
    This behaviour is illustrated in figure~\ref{fig:extinction_32_5} on the basis of the drag timeseries involved in the experiment of figure~\ref{fig:comparaison_ams_return_time_instant_a}.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{ams/iter_181}
    \caption{Visualisation of the drag timeseries corresponding to the set of trajectories in the ensemble, at different iterations along the algorithm. In this experiment, the \ac{tams} is used with the instantaneous drag $f_d$ as a score function. Trajectories have a duration $T_a = 5\tau_c$ and their number is $N_c = 32$.
    One can see that, as the number of iterations increases, the number of independent resampled trajectories drastically decreases until extinction at iteration $181$. The timeseries corresponding to the two initial trajectories exhibiting the highest fluctuations are displayed in colour. In all four figures, colour is inherited from the parent trajectory. It illustrates that the two strongest initial trajectories quickly become predominant in the ensemble, as the other are discarded.
    As can be seen in figure~\ref{fig:subfigc}, trajectories only separate well after the maximum is reached. Therefore, resampling the blue trajectories based on the red trajectories can only change the overall maximum by a very small amount. Consequently, blue trajectories are discarded one after the other, each time resampled into another instance of the red trajectory. This new instance has roughly the same maximum as the others.}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{illustration_IS}
  \caption{\textbf{(a)}: Importance sampling for the time-averaged drag acting on the obstacle embedded in the test flow. The drag is averaged over $T=10\tau_c$. 
  The \ac{gktl} algorithm is used with $N_c = 16384$ copies and $T_a = T= 10\tau_c$ for three increasing values of the bias $k$. Additionally, the cloning period is $\tau = \tau_c/2$, resulting in $M=20$ iterations of the evolution/selection procedure. Note that in this particular example the last cloning stage at $t_{19}$ is not performed.
  As $k$ is increased, the sampled \ac{pdf} is shifted towards extreme values.
  Along the X-axis we display the fluctuation $F'_{T} = F_{T} - \overline{F_{T}}$, where the average $\overline{F_{T}}$ and standard deviation $\sigma_{T}$ have been computed over a timeseries spanning $10^6\tau_c$.
  One can see that the distribution for $k=0.03$ is peaked for a particular value of the fluctuation. This indicates that a significant part of the sampled trajectories actually overlap over the major part if their history.
  A a result, the average drag only differ by a small amount.}
\end{figure}

>>>>

\documentclass[pre,aps,floatfix,10pt,superscriptaddress, notitlepage]{revtex4-1}
\pdfoutput=1
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage[svgnames]{xcolor}
\usepackage{graphicx}
\usepackage{acro}
\usepackage{subfig}
\usepackage{caption}
\graphicspath{{./figures/}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{illustr_vort/illustration_vorticity_tf2}
  \caption{Typical vorticity field in the computational domain. The square obstacle is represented by the gray area in the center of the channel.}
\end{figure}
%% Description de la géométrie
We consider the interaction of a two dimensional turbulent channel flow with a square cylinder, illustrated in figure~\ref{fig:computational_domain}.
A constant parabolic velocity profile is imposed at the inlet of the channel and turbulence is
generated by means of a grid.
A square obstacle is mounted at the center of the channel.
Eddies are created in the vicinity of the grid with a typical size that correspond to the step of the grid.
As they are advected downstream, eddies interact with each other and grow in size, until they interact with the obstacle.
The distance separating the obstacle from the grid is such that the typical size of the eddies it interacts with is close to the size of the obstacle itself.
The flow in the vicinity of the outlet is regularized by means of a \textit{sponge layer}~\cite{ref1,ref2}, \textit{i.e.} a region where the viscosity is progressivaly increased.
Such sponge layer facilitates the implementation of an open boundary at the outlet, where a zero momentum flux along the mean-flow direction in imposed.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{typical_drag_signal/typical_drag_signal.png}
  \caption{Typical temporal evolution of the drag acting on the square cylinder pictured in figure~\ref{fig:computational_domain}. The correlation time $\tau_c$ is defined further in this text and correspond to the typical fluctuation timescale of the drag.}
  \label{fig:typical_drag_signal}
\end{figure}

@@

\begin{figure}
  \centering
    \subfloat[\ac{pdf} for the drag fluctuations $f'_d$]{\label{fig:pdf_drag_a}\includegraphics[width=.5\linewidth]{./PDF_drag/PDF_drag.png}}
    \subfloat[Autocorrelation function of the the instantaneous drag $f_d$]{\label{fig:pdf_drag_b}\includegraphics[width=.5\linewidth]{autocorr_drag/autocorr_drag.png}}  
  \caption{\textbf{(a)} \ac{pdf} describing the statistics of the instantaneous drag fluctuations $f'_d = (f_d - \bar{f_d})/\sigma$. This \ac{pdf} has been estimated on the basis of a timeseries spanning $T_{tot} = 10^6 \tau_c$. $\bar{f_d}$ and $\sigma$ denote the average and the standard deviation computed over the whole timeseries, respectively. The linear fits highlight the exponential behaviour of the the \ac{pdf} for rare events. \textbf{(b)} Autocorrelation function for the instantaneous drag $f_d$, defined as $(\mathbb{E}[f_d(t+\tau)f_d(t)]-\mathbb{E}[f_d]^2)/\sigma^2$ and estimated from a timeseries spanning $T_{tot} = 10^6 \tau_c$. This figure shows the exponential decay of the correlations over time.}
  \label{fig:pdf_drag}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.6\linewidth]{return_time/return_time.png}
  \caption{Drag fluctuation amplitude as a function the corresponding return time. The return time $r(a)$ is the typical timescale of occurrence of a fluctuation of amplitude larger than $a$.}
  \label{fig:return_time_instant}
\end{figure}
\subsection{Instantaneous drag}
\label{sec:instantaneous_drag}

\subsubsection{Contribution of forebody and base pressure fluctuations to the overall drag fluctuation}
\label{sec:forebody_and_base_contribution}
In section~\ref{sec:test_flow}, we pointed out that typical drag fluctuations mainly originate from fluctuations of the forebody pressure, \textit{i.e.} pressure fluctuations resulting from the upstream turbulent flow.
We now investigate the relative contribution of forebody and base pressure fluctuations to the overall drag fluctuations, in the case of the sampled \textit{extreme} drag fluctuations.
Let $(t^{\star}, f_d^{\star})$ be an extreme drag event.
In the following we consider the effective fluctuation $\tilde{f}_d^{\star} = f_d^{\star} - \langle f_d \rangle$.
It can be further decomposed into 
\begin{equation}
  \tilde{f}_d^{\star} = \tilde{p}_{fb}^{\star} - \tilde{p}_{base}^{\star},
\end{equation}
where $\tilde{p}_{fb}^{\star}$ and $\tilde{p}_{base}^{\star}$ denote the fluctuation of the forebody pressure and base pressure, respectively, that is $\tilde{p}_{base}^{\star} = p_{base}^{\star} - \langle p_{base} \rangle$ .
Figure~\ref{fig:contribution_forebody_and_base_pressure} shows the relative contributions $\tilde{p}_{base}^{\star}/\tilde{f}_d^{\star}$ and $\tilde{p}_{fb}^{\star}/\tilde{f}_d^{\star}$ to the overall drag fluctuation for the base and forebody pressure fluctuations, respectively.  
\begin{figure}
  \centering
  \includegraphics{pressure_ratio/pressure_ratio.png}
  \label{fig:pressure_ratio}
\end{figure}
It shows that among the 104 sampled extreme events, the base pressure fluctuation typically contributes for $80\%$ of the overall drag fluctuation.
By contrast with typical drag fluctuations, extreme fluctuations of the drag acting on the square cylinder are dominated by the variation of the pressure in the vicinity of the base of the obstacle.
In addition, figure~\ref{fig:pressure_ratio} hints that, the larger the fluctuation, the more important is the contribution of the base pressure fluctuation, relatively to the forebody pressure fluctuation.

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{illustr_extrms_vorticity/illustr_extrms_vorticity.png}
  \caption{\label{fig:top_4_events_vorticity} Vorticity field at $t=t^{\star}$ for the four highest drag fluctuations in the timeseries. The corresponding drag timeseries can be found in figure~\ref{fig:extremes_timeseries}.
    The high value for the drag results from the formation of a strong negative (red) vortex inducing a pressure drop at the base of the obstacle. The formation of such a structure is aided by important vorticity production at the bottom boundary of the obstacle coupled with the influence of positive vorticity in the vicinity of the base.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.5\linewidth]{illustr_density_streamlines/illustr_density_streamlines.png}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.5\linewidth]{timeseries_extremes/timeseries_extremes.png}
\end{figure}

% \begin{figure}
%   \centering
%   \begin{minipage}{0.85\linewidth}
%     \begin{tabular}{c|c}
%     \subfloat[$f'_d = 11.6\sigma$]{\label{fig:top_4_events_vorticity_a}\includegraphics[width=0.4\linewidth]{event_95_vort.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$f'_d = 11.2\sigma$]{\includegraphics[width=0.4\linewidth]{event_69_vort.png}} \\
%     \hline
%     \subfloat[$f'_d = 10.6\sigma$]{\includegraphics[width=0.4\linewidth]{event_53_vort.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$10\sigma$]{\includegraphics[width=0.4\linewidth]{event_20_vort.png}}
%     \end{tabular}
%   \end{minipage}
% \begin{minipage}[h]{0.1\linewidth}
%   \centering
%   \includegraphics[width=\linewidth]{scale_vorticity.png}
% \end{minipage}
% \caption{\label{fig:top_4_events_vorticity} Vorticity field at $t=t^{\star}$ for the four highest drag fluctuations in the timeseries. The corresponding drag timeseries can be found in figure~\ref{fig:extremes_timeseries}.
%   The high value for the drag results from the formation of a strong negative (red) vortex inducing a pressure drop at the base of the obstacle. The formation of such a structure is aided by important vorticity production at the bottom boundary of the obstacle coupled with the influence of positive vorticity in the vicinity of the base.}
% \end{figure}

@@

% Modify the TAMS to fit the phenomenology ?
A promising perspective is to adapt the \ac{tams} to dynamics for which the Lyapunov time is larger than the typical duration of extreme events, such as the convective flow involved in this work.
In the original \ac{tams}, at later stages of the algorithm, new trajectories are resampled starting from points very close to the maximum of the parent trajectory.
Resampled trajectories have no chance to display a significantly higher maximum as they overlap their parent trajectory over the Lyapunov timescale.
As an example, the resampling procedure could be modified so that new trajectories are resampled roughly a Lyapunov time \textit{before} the maximum is attained.
In this way, it gives the opportunity for new events, associated to a higher fluctuations, to occur.
However, such modification(s) of the resampling procedure must be implemented with care, so as to preserve the mathematical properties of the \ac{ams} and \ac{tams}.
\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{illustr_AMS/figure_AMS}
  \caption{Illustration of one selection-mutation step in the \ac{ams} algorithm for the computation of the probability that an observable $A:\mathbb{R}^d\to \mathbb{R}$  reaches values larger than $Q$ over a trajectory of duration $T_a$.}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{AMS_OU/AMS_OU.png}
    \caption{Illustration of the efficiency of the \ac{tams} algorithm with respect to direct sampling. The amplitude of fluctuations for the \ac{ou} process~\eqref{eq:OUprocess_chap_ams} are represented along the Y-axis. Along the X-axis is represented the typical computational cost required to sample fluctuations of the corresponding amplitude in both the \ac{tams} and direct sampling. In the latter, the typical computational cost is simply the return time $r(a)$. The computational cost associated to a level $a$ is the \ac{tams} is denoted by $C(a)$. The orange line represents the evolution of the level $\mathcal{Q}_j^{\star}$ as a function of the cost $C(a)$. The blue stars represent the maximum of $x(t)$ over the resampled trajectory \emph{after} it is resampled, that is at iteration $j+1$. Finally, the solid black line is the analytical solution for the return time of amplitude $a$~\cite{lestang_computing_2018}.}
  \label{fig:comparaison_temps_de_retour}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{AMS_drag_resampling/AMS_drag_resampling.png}
    \caption{Maximum of the instantaneous drag along the resampled trajectories, denoted by $\tilde{f}_d^{(j)}$, as a function of the corresponding computational cost $C_j$, defined in~\eqref{eq:comp_cost_iterations}. In both figures, the \ac{tams} is iterated until extinction. 
    The solid black line indicates the typical fluctuation amplitude $a$ as a function of the corresponding  \textit{return time} $r(a)$. It is the typical timescale of occurrence of fluctuations above $a$. Furthermore, the square markers depict the maximum $\tilde{f}_{d,n}^{(0)},\,\, 1\leq n \leq N_c$ over the initial trajectories.
    This figure illustrates that in both experiments the \ac{tams} does not improve the sampling of rare fluctuations. On can see that the maximum values among the resampled trajectories concentrates on values already sampled over the initial trajectories. Eventually, extinction is reached as the algorithm is unable to generate a fluctuation higher than the maximum fluctuation in the initial ensemble of trajectories.
    This behaviour is illustrated in figure~\ref{fig:extinction_32_5} on the basis of the drag timeseries involved in the experiment of figure~\ref{fig:comparaison_ams_return_time_instant_a}.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{AMS_drag_trajectories/AMS_drag_trajectories.png}
    \caption{Visualisation of the drag timeseries corresponding to the set of trajectories in the ensemble, at different iterations along the algorithm. In this experiment, the \ac{tams} is used with the instantaneous drag $f_d$ as a score function. Trajectories have a duration $T_a = 5\tau_c$ and their number is $N_c = 32$.
    One can see that, as the number of iterations increases, the number of independent resampled trajectories drastically decreases until extinction at iteration $181$. The timeseries corresponding to the two initial trajectories exhibiting the highest fluctuations are displayed in colour. In all four figures, colour is inherited from the parent trajectory. It illustrates that the two strongest initial trajectories quickly become predominant in the ensemble, as the other are discarded.
    As can be seen in figure~\ref{fig:subfigc}, trajectories only separate well after the maximum is reached. Therefore, resampling the blue trajectories based on the red trajectories can only change the overall maximum by a very small amount. Consequently, blue trajectories are discarded one after the other, each time resampled into another instance of the red trajectory. This new instance has roughly the same maximum as the others.}
\end{figure}

@@

\begin{figure}
  \centering
%  \includegraphics[width=0.7\linewidth]{illustration_IS}
  \caption{\textbf{(a)}: Importance sampling for the time-averaged drag acting on the obstacle embedded in the test flow. The drag is averaged over $T=10\tau_c$. 
  The \ac{gktl} algorithm is used with $N_c = 16384$ copies and $T_a = T= 10\tau_c$ for three increasing values of the bias $k$. Additionally, the cloning period is $\tau = \tau_c/2$, resulting in $M=20$ iterations of the evolution/selection procedure. Note that in this particular example the last cloning stage at $t_{19}$ is not performed.
  As $k$ is increased, the sampled \ac{pdf} is shifted towards extreme values.
  Along the X-axis we display the fluctuation $F'_{T} = F_{T} - \overline{F_{T}}$, where the average $\overline{F_{T}}$ and standard deviation $\sigma_{T}$ have been computed over a timeseries spanning $10^6\tau_c$.
  One can see that the distribution for $k=0.03$ is peaked for a particular value of the fluctuation. This indicates that a significant part of the sampled trajectories actually overlap over the major part if their history.
  A a result, the average drag only differ by a small amount.}
\end{figure}
